The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
add description for step-47.

\author[13]{Zhuoran Wang}
\affil[13]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@colostate.edu}}}         
\renewcommand{\labelitemi}{--}

@@

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-47}
\todo[inline]{Zhuoran to write}
\item \texttt{step-50}
  \todo[inline]{Timo/Conrad/... to write}

>>>>

\author[13]{Zhuoran Wang}
\affil[13]{Department of Mathematics, Colorado State University, Fort Collins,
          CO 80523-1874, USA.
{\texttt{zhrwang@math.colostate.edu}}}
\renewcommand{\labelitemi}{--}

@@

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-47} solves the biharmonic equation with the
  clamped boundary condition. This program is based on the $C^0$ interior
  penalty method for fourth order problems. In order to overcome
  shortcomings of classical approaches, this method uses $C^0$ Lagrange finite
  elements and introduces ``jump`` and ``average`` on interfaces of elements.
  The resulting system is obtained through integration by parts, symmetrization,
  and stabilization. Appropriate choices for the penalty parameter are
  discussed based on numerical results.

\item \texttt{step-50}
  \todo[inline]{Timo/Conrad/... to write}
